%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Researcher} % Role
    {Sparse Decomposition Machine Learning Research{\normalfont, \href{https://github.com/salevin/atari-psd}{github.com/salevin/atari-psd}}} % Title
    {Goucher} % Location
    {2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Applied an unsupervised learning model trained to do machine vision to a video-game-playing neural network.}
        \item {Written in lua using the Torch machine learning framework. Used cutorch to run models on a GTX Titan graphics card.}
        \item {An adaptation of Google DeepMind's Atari-Q-Learner}.
        \item {Separated the original convolutional neural net into an unsupervised network and a fully connected network.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Dev \& Club President} % Role
    {Climbing Club Web App{\normalfont, \href{http://www.goucherclimbs.com/}{goucherclimbs.com}} } % Title
    {Goucher} % Location
    {2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Had to schedule times to go climbing with many members who have varying schedules.}
        \item {With student credit, I used a Digital Ocean virtualized server to create a web app for scheduling.}
        \item {Created with nodejs, expressjs, ejs and bootstrap. It allows members to input their availability.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
