%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Senior Software Engineer} % Job title
    {Credit Karma} % Organization
    {Oakland, CA} % Location
    {January 2019 - June 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {\bfseries Data Architecture Team}
          \vspace{2em}
          \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Built and scaled Vertex Feature Store integrations, including online stores, registries, and monitoring APIs, enabling production ML workflows across multiple domains.}
          \item {Designed and optimized Dataflow pipelines (feature deletion, fast batch ingestion, containerized SMB exports) improving reliability and reducing processing latency.}
          \item {Automated Airflow workflows with custom DAGs, retries, and alerting, improving data pipeline stability and reducing operational overhead.}
          \item {Developed Terraform/Terragrunt infrastructure for Vertex and Composer, streamlining environment provisioning and access control.}
          \item {Enhanced observability and reliability by adding monitoring, circuit breakers, and Slack alerting, reducing downtime and improving incident response.}
          \item {Contributed to data platform libraries and services (Alchemy, Lightspeed, IDL, lineage tools) supporting large-scale recommendation and finance data systems.}
          \item {Improved CI/CD pipelines with validation pipelines, CCI fixes, and automated testing, accelerating deployment velocity and reducing failures.}
          \end{cvitems}
          \vspace{1em}
          \item {\bfseries Credit Karma Money Team}
          \vspace{2em}
          \begin{cvitems} % Description(s) of tasks/responsibilities
              \item {Designed and implemented offline networth tracking using event topic subscription service.}
              \item {Added account value fallbacks, adding data consistency.}
              \item {Built data quality and observability metrics and dashboards.}
          \end{cvitems}
          \vspace{1em}
          \item {\bfseries Offer Creation Platform Team}
          \vspace{2em}
          \begin{cvitems} % Description(s) of tasks/responsibilities
              \item {Built and maintained a complex react app for creating, modifying, and viewing credit cards and offers shown within Credit Karma.}
              \item {Worked on a graphql gateway for handling changes to these offers and routing to the correct services.}
              \item {Built and scaled scala services deployed on kubernetes, requiring high uptime with extensive monitoring and failover.}
              \item {Worked on internal SDKs allowing services to use packaged scala code through sbt dependencies.}
          \end{cvitems}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {Serena and Lily} % Organization
    {Sausalito, CA} % Location
    {March 2018 - December 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with multiple teams to move entire ecommerce development inhouse}
        \item {Updated deprecated front end librarys and development process}
        \item {Started the transition to CommonJS controllers from deprecated SaleForce Demandware Pipelines}
        \item {Integrated new analytics, AB testing, and integration testing applications}
      \end{cvitems}
    }



  \cventry
    {Intern Software Engineer} % Job title
    {Microsoft} % Organization
    {Dublin, Ireland} % Location
    {Summer 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Shadowed dev teams in a group working on a CMS (content management service) for MSN news}
        \item {Main technologies were TypeScript/Angular/AJAX}
        \item {Single Page Angular-js site, that used a c\# middle tier to deal with certs and calls to the Backend SQL database}
        \item {Worked on a local build of the site and have an accepted code merge onto the production branch of their TFS version control server}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
